% ════════════════════════════════════════════════════════════════════════════
\section{Model}
\label{sec:model}
% ════════════════════════════════════════════════════════════════════════════

\subsection*{Notation}

\noindent The symbols below recur throughout; each is defined in full where it is
introduced, and all are gathered here for reference.

\vspace{4pt}

\begingroup\small
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\toprule
\multicolumn{2}{@{}l}{\textbf{Principals, assets, economics}}\\
\midrule
$\Victim,\ \Attacker$ & holder (victim) and coercer (attacker) \\
$K$ & master secret gating the asset \\
$W$ & value of the asset to $\Victim$ \\
$c$ & expected disutility to $\Attacker$ of killing $\Victim$ \\
$\pi$ & $\Victim$'s \emph{pivotality} --- win-probability $\Attacker$ gains by removing $\Victim$ \\
\addlinespace
\multicolumn{2}{@{}l}{\textbf{Adversary, game, safety}}\\
\midrule
WDY & the Wrench--Dolev--Yao adversary, fixed by clauses \ref{d:kerckhoffs}--\ref{d:nodelegatecoerce} (Assumption~\ref{ass:power}) \\
$p_A$ & probability $\Attacker$ reaches $K$ after the encounter; \emph{gray} iff $0<p_A<1$ \\
$t$ & coercion-time budget (how long $\Attacker$ can sustain coercion) \\
$G$ & protocol time-gate (enforced latency to complete the derivation) \\
$\mathsf{Corr}$ & residual-window event: the points $\Victim$ has surrendered so far are correct (\S\ref{sec:residual}) \\
$\mathsf{Esc}$ & residual-window event: the ${\approx}1$--$2$ min shaved by brute-forcing the last points decides escape from the scene (\S\ref{sec:residual}) \\
\addlinespace
\multicolumn{2}{@{}l}{\textbf{Construction (TGPO orbit)}}\\
\midrule
$\sigma$ & public, precomputation-resistant timechain salt (Namtso) \\
$\Hcheap,\ \Hhard$ & cheap hash; memory- and depth-hard (Argon2-class) hash \\
$o_i$ & orbit state at stage $i \in \{0,\dots,N\}$; $o_i = \Hhard(u_i)$ (with $o_0 = \Hcheap(\sigma)$); $N{+}1$ stages total \\
$N$ & number of \emph{deep} stages --- those requiring at least one memory- and depth-hard hash ($\Hhard$) to derive \\
$u_i$ & $\Hcheap(o_{i}\|\Sh_{i})$: commitment of the wiped values $o_{i}$ and $\Sh_{i}$ \\
$\Sh_i$ & Shamir polynomial at stage $i$; $k_i$ of its points reconstruct it \\
$p_{i,j},\ \theta_{i,j}$ & point $j$ of stage $i$; parameters for fractal $j$ of stage $i$ \\
$k_i$ & Shamir threshold at stage $i$ ($k_i \ge 2$) \\
$\sftstar$ & $2^{64}$ memory- and depth-hard evaluations (infeasible) \\
\bottomrule
\end{tabularx}
\endgroup

\subsection{Principals and capabilities}

\begin{definition}[Principals]
The \textbf{holder} $\Victim$ possesses (in memory and on devices) whatever is
needed to reach a master secret $K$ that gates an asset. The \textbf{coercer}
$\Attacker$ seeks $K$. Optional \textbf{heirs} or \textbf{delegates} may hold
partial capability on $\Victim$'s behalf.
\end{definition}

\begin{assumption}[Kerckhoffs, premise~0]\label{ass:kerckhoffs}
$\Attacker$ knows the protocol in full: all algorithms, all source, $\Victim$'s
setup topology, and every in-scope parameter. Only the protocol \emph{secrets}
are hidden. Every result below is proved \emph{against} such an $\Attacker$;
security by obscurity is assumed to contribute nothing.
\end{assumption}

\begin{assumption}[The Wrench--Dolev--Yao (WDY) adversary]\label{ass:power}
The \textbf{Wrench--Dolev--Yao (WDY)} adversary inherits the
Dolev--Yao~\cite{dolev-yao} intruder \emph{on the wire} --- it sees all transmitted
plaintext and ciphertext --- but departs from it in two ways that matter here. It is
\emph{computational}, not symbolic: Dolev--Yao's perfect-cryptography idealization is
replaced by the feasibility line (Stipulation~\ref{ass:feas}), so ``cannot break the
cipher'' becomes ``cannot exceed its work budget''. And it is extended \emph{past the
wire} with the physical capabilities Dolev--Yao omits --- device seizure and a bounded
coercion oracle over the holder: the \emph{wrench} the name records. WDY is fixed by:
\begin{enumerate}[nosep,leftmargin=2.4em,start=0,label=\textbf{D\arabic*.},ref=D\arabic*]
  \item\label{d:kerckhoffs} \textbf{Kerckhoffs.} $\Attacker$ knows the protocol,
        $\Victim$'s setup topology, and every in-scope parameter
        (Assumption~\ref{ass:kerckhoffs}).
  \item\label{d:compute} \textbf{Bounded compute.} $\Attacker$'s computation is bounded by the
        feasibility line (Stipulation~\ref{ass:feas} below): $2^{32}$ cheap
        evaluations feasible, plain $2^{64}$ cheap at the border (the softest
        number), and $2^{64}$ memory-hard ($\sftstar$) and $2^{96}$ cheap both
        infeasible. This is what
        replaces ``unbounded'': the wall-clock custody window bounds
        $\Attacker$ crudely, the feasibility line \emph{sharply}.
  \item\label{d:frequency} \textbf{Frequency ceiling.} There is a ceiling on how much faster
        $\Attacker$'s hardware evaluates a computation than $\Victim$'s. So an
        entropy-preserving hash with enough \emph{non-parallelizable} steps ($\Hhard$)
        lets $\Victim$'s setup impose an \emph{arbitrarily long} latency on
        $\Attacker$ per evaluation --- at the price of a proportionally longer
        latency on $\Victim$. This is what makes the time-gate meaningful:
        $\Attacker$ can neither parallelize nor out-clock its way past a sequential
        memory-hard chain.
  \item\label{d:subjugation} \textbf{Complete subjugation.} This is an information-security model, not
        a study of physical violence versus physical defense; we do not model
        $\Attacker$'s coercive power against $\Victim$'s resistance. For
        simplicity, and to make the argument \emph{a fortiori}, we assume that
        from the onset of the attack until $\Attacker$ releases $\Victim$,
        $\Attacker$ meets \emph{no resistance whatsoever} and enjoys $\Victim$'s
        \emph{full cooperation}. The sole qualification --- \emph{feigned}
        cooperation in the residual window --- is, as we argue there
        (\S\ref{sec:residual}), of residual importance.
  \item\label{d:seizure} \textbf{Co-located device seizure.} All of $\Victim$'s devices \emph{at
        the attack site} are immediately seized --- vault blobs, time-lock blobs,
        commitment scripts, review schedules. A single WDY encounter has one
        \emph{site}; devices and principals at \emph{other} sites lie beyond its
        reach within the bounded window --- the opening a \emph{geographic}
        defense exploits (\S\ref{sub:fourprops}).
  \item\label{d:explicit} \textbf{Explicit-secret seizure.} All of $\Victim$'s \emph{explicit}
        (non-tacit) authenticating secrets are immediately seized.
  \item\label{d:notacit} \textbf{No tacit seizure.} $\Victim$'s \emph{tacit} entropy-carrying 
        secrets --- the points --- are captured by seizure \emph{if and only if} they are
        \emph{available} in transmissible form at the moment of attack (materialized,
        and not wiped before $\Victim$ is subdued) --- that is, exactly when the
        tacitness fails to be effective. When it \emph{is} effective they are not:
        by \ref{d:subjugation} this is a genuine \emph{incapacity to transmit}, not
        any unwillingness --- even a fully cooperating $\Victim$ cannot hand them
        over, because they are recognizable but non-transmissible. This and
        \ref{d:noperceptual} are the operational restatement, in the adversary
        model, of the tacit-knowledge premise (Assumption~\ref{ass:tkba}).
  \item\label{d:noperceptual} \textbf{No perceptual-parameter seizure.} As with
        the tacit entropy-carrying secrets (\ref{d:notacit}), $\Victim$'s
        perceptual-oracle parameters --- the deep fractals --- are seized \emph{iff}
        they are available at the moment of attack; when the tacitness is effective 
        they are not. As in \ref{d:notacit}, and by \ref{d:subjugation}, this is 
        incapacity under full cooperation, not withholding: the deep fractal parameters 
        are regenerated only by walking the memory-hard chain, so a willing $\Victim$ 
        has nothing to dictate (Assumption~\ref{ass:tkba}).
  \item\label{d:nodelegatecoerce} \textbf{No remote-delegate coercion.} A remote
        delegate --- a party holding rescue capability on $\Victim$'s behalf beyond
        the attack site (\ref{d:seizure}) --- is past $\Attacker$'s \emph{remote}
        coercive reach: from the encounter with $\Victim$, $\Attacker$ cannot compel
        it to surrender or act on its state. Without this a delegated defense is
        vacuous. Real delegates span a spectrum of coercion-compliance; collapsing it
        to a clean ``cannot be reached'' is a deliberate simplification --- the kind
        that makes the \emph{a fortiori} argument possible, at the cost of reality's
        shades.
\end{enumerate}
The \emph{only} channel to the tacit material withheld by \ref{d:notacit}--\ref{d:noperceptual} is a
\textbf{bounded coercion oracle}: $\Attacker$ extracts it through the cooperating
$\Victim$ (\ref{d:subjugation}) over a bounded duration $t$ --- the adversary's
\textbf{coercion-time budget}, the maximum wall-clock time for which it can sustain coercion,
calibrated against the incident durations in the registry~\cite{lopp-attacks}.
Cooperation is genuine throughout by \ref{d:subjugation}; the one exception, \emph{feigned}
cooperation, is confined to the residual window (\S\ref{sec:residual}).
\end{assumption}

\begin{remark}[The two non-seizure clauses coincide for design]\label{rem:tacit-coincide}
For protocol-design purposes the tacitness of the entropy-carrying secrets
(\ref{d:notacit}) and that of the perceptual-oracle parameters
(\ref{d:noperceptual}) are logically equivalent. If the parameters were
transmissible, a wrench attack would seize them --- and, available within that
\emph{same} encounter, they would then serve to seize the entropy-carrying points
themselves; so non-tacit parameters force non-tacit points. Conversely, if the
points were somehow transmissible without the parameters ever being available,
then the tacitness of the parameters is irrelevant, the points having already
fallen. Either way the binary question ``does a single seizure reach $K$?'' turns
on the two clauses together, and the model may treat them as one.
\end{remark}

\begin{remark}[Where the distinction still matters]\label{rem:tacit-quantitative}
The distinction can nonetheless matter for a \emph{quantitative} refinement --- a
statistical distribution of the wall-clock needed to coerce either (up to sufficient
number of most-significant bits) given $\Attacker$'s coercion time budget $t$ 
(Definition \ref{def:priced}). Still, a secret that is \emph{theoretically} transmissible, 
but only with pen and paper, an adversarial fork of the application, and long hours 
to days of focused mental effort under perfect $\Attacker$--$\Victim$ cooperation, 
is essentially as good as ideal. Until empirical studies of TKBA (Assumption~\ref{ass:tkba}) 
are done, the actual relevance of that nuance is purely speculative.
\end{remark}

\subsection{The feasibility line}

Asymptotic ``hard'' and ``easy'' are useless against a fixed, resourced
attacker; we replace them with two engineering stipulations that fix what
\emph{feasible} means and turn the lemmas into concrete bounds.

\begin{stipulation}[Feasibility line]\label{ass:feas}
Let a \emph{cheap} evaluation be one call to a non-memory-hard hash $\Hcheap$,
and a \emph{hard} evaluation one call to an hours-scale Argon2-class function
$\Hhard$ whose cost is a large number of \emph{non-parallelizable} steps ---
\emph{memory- and depth}-hard,\footnote{\emph{Depth-hard} is meant more sharply
than \emph{sequential} or \emph{non-parallelizable} alone: the cost is a
non-parallelizable computation with a \emph{deliberately large number of steps} ---
a long sequential \emph{depth} --- the parallelism-resistance axis of
\emph{depth-robust} memory-hard functions~\cite{depth-robust} --- that $\Attacker$
can neither parallelize away nor out-clock past (\ref{d:frequency}). We also weighed \emph{memory- and
sequentiality-hard} (accurate but clumsy) and \emph{memory- and
iteration-count-hard} (which names the step \emph{count} rather than its
non-parallelizable structure); \emph{depth} is the single noun that carries both
the seriality and the magnitude, and it parallels \emph{memory}.} so
$\Attacker$'s bounded speed advantage (\ref{d:frequency})
cannot amortize it~\cite{argon2}.
\begin{enumerate}[nosep,leftmargin=2.2em,label=\textbf{S\arabic*},ref=S\arabic*]
  \item\label{s:feasible} \textbf{(feasible).} $2^{32}$ cheap evaluations are within
        $\Attacker$'s budget.
  \item\label{s:infeasible} \textbf{(infeasible).} $2^{64}$ \emph{hard} evaluations --- written
        $\mathbf{64^{*}}$ --- are beyond it.
  \item\label{s:infeasiblec} \textbf{(infeasible).} $2^{96}$ cheap evaluations are beyond it.
\end{enumerate}
The star denotes this memory- and depth-hardness and attaches to \emph{any}
bit-count --- $32^{*}, 64^{*}, 96^{*}, \dots$ --- each meaning that many $\Hhard$
evaluations, not just $64^{*}$.
\end{stipulation}

\noindent We keep the star rather than fold it into an equivalent bit-count because
memory- and depth-hardness has \emph{three} distinct consequences, only the first of
which a bit-count could absorb: it \textbf{(1)}~inflates the brute-force cost --- this
alone \emph{could} be traded for a stipulated increase in bits; \textbf{(2)}~imposes a
wall-clock \emph{derivation time} on each evaluation, which the bounded coercion
window $t$ (\ref{d:subjugation}) cannot outrun; and \textbf{(3)}~rules out the quantum
(Grover) speed-up (\S\ref{sec:quantum}). A pure bit-count captures only~(1); the star
carries all three.

Two currencies span the gap between them. \emph{Entropy} buys $32 \to 64$: a
second independent 32-bit stage. But plain $2^{64}$ \emph{cheap} work still sits
at the border of a resourced attacker's reach (hours), so the $64 \to \sftstar$
step must be bought by \emph{memory-hardness} --- which is why the gating
function has to be Argon2-class. We refer to plain cheap $2^{64}$ throughout as
the \emph{softest number}: it must be named explicitly wherever it is invoked,
never silently treated as infeasible.

\subsection{The tacit-knowledge premise}

The construction of \S\ref{sec:gw} rests the secret on \emph{tacit} knowledge.
We state the premise abstractly here; \S\ref{sec:gw} instantiates it.

\begin{assumption}[Tacit knowledge, TKBA]\label{ass:tkba}
The secret is a set of fractal locations that are \emph{recognizable but not
transmissible}.
\begin{itemize}[nosep,leftmargin=1.4em]
  \item \textbf{TKBA$_1$.} A point is non-transmissible without the fractal
        parameters that render it; $\Victim$ cannot dictate it in the abstract.
  \item \textbf{TKBA$_2$.} The \emph{deep} fractal parameters are not a
        hand-overable artifact; producing them requires walking a memory-hard
        chain, before which later locations do not exist.
\end{itemize}
\end{assumption}

\begin{remark}[TKBA restates the tacit-seizure clauses]\label{rem:tkba-restates}
Assumption~\ref{ass:tkba} is not an independent hypothesis: it is
clauses~\ref{d:notacit}--\ref{d:noperceptual} lifted out of the adversary model and
stated as a premise on the secret. The clauses say $\Attacker$ cannot seize the
tacit points or the perceptual parameters even under full cooperation
(\ref{d:subjugation}); TKBA says the same thing about the secret itself ---
recognizable but not transmissible --- with no adversary mentioned. They are two
faces of one assumption (exactly as \ref{d:kerckhoffs} and
Assumption~\ref{ass:kerckhoffs} are two faces of Kerckhoffs), and by
Remark~\ref{rem:tacit-coincide} the two clauses are themselves one. We keep both
forms because each is the natural one in its place --- the premise where the
construction is motivated (\S\ref{sec:gw}), the adversary clause where seizure is
reasoned about.
\end{remark}

