% ════════════════════════════════════════════════════════════════════════════
\section{Construction --- the Time-Gated Perceptual Oracle (clears by removing the race)}
\label{sec:gw}
% ════════════════════════════════════════════════════════════════════════════

We now exhibit a construction that clears Criterion~\ref{prin:nga} by the first
route of Corollary~\ref{cor:reach} --- the \emph{tacit} route that
Corollary~\ref{cor:fourprops} shows is forced by holding all Four Properties at
once: it admits \emph{no feasible seizure path}, so custody remains individual.
We call it the \textbf{Time-Gated Perceptual Oracle}
(TGPO) --- \emph{time-gated} for the memory-hard orbit and time-lock puzzle,
\emph{perceptual} for the tacit fractal recognition, \emph{oracle} for its
evaluate-only-by-the-holder semantics; it is the coercion-resistance protocol at
the core of the Great Wall / Great Wallet self-custody application. We give here the
parts the theorem needs; the concrete instantiation parameters --- the
memory-hard cost tiers, iteration factoring, and the timechain salt --- are
specified in the Great Wall Core design document~\cite{gw-design}.

\subsection{The orbit}

Let $\Hcheap$ be a cheap, entropy-preserving one-way hash and $\Hhard$ a
memory-hard (Argon2-class) hash of tunable cost. Let $\sigma$ be a public,
precomputation-resistant \emph{timechain salt} whose cross-user amortization is
negligible (the companion Namtso primitive~\cite{gw-timechain-salt}). Define an
\textbf{orbit} of $N$ deep stages (Figure~\ref{fig:orbit}):
\begin{align}
  o_0 &= \Hcheap(\sigma),                && \\
  u_i &= \Hcheap(o_{i} \,\|\, \Sh_{i}),  && 0 \le i \le N-1, \\
  o_i &= \Hhard\!\big(\, u_{i-1} \,\big), && 1 \le i \le N, \\
  K_i &= \Hcheap(o_i \,\|\, \Sh_i),      && 0 \le i \le N,
  \label{eq:orbit}
\end{align}
where the raw inputs $\{o_{i-1}, \Sh_{i-1}\}$ are \textbf{wiped} in the instant
between the cheap inner hash and the long memory-hard step. Computing
$u_{i-1} := \Hcheap(o_{i-1}\|\Sh_{i-1})$ first (instant), wiping, then running the
long $o_i := \Hhard(u_{i-1})$, means the raw prior orbit point and Shamir secret exist
only momentarily --- not across the whole memory-hard window. This directly
shrinks the window in which $\{o_{i-1},\Sh_{i-1}\}$ is seizable (\ref{d:seizure}),
and is the reason not to use $\Hhard(o_{i-1}\|\Sh_{i-1})$ directly.

\emph{On notation.} $\Hcheap$ and $\Hhard$ are \emph{generic} designations --- any
suitable cheap, and memory- and depth-hard (Argon2-class), instantiation serves.
Note that $u_i$ and $K_i$ share the formula $\Hcheap(o_i\|\Sh_i)$; they are
nonetheless \emph{distinct} objects, separated by \emph{role} --- $u_i$ is consumed
by the next memory-hard step, whereas $K_i$ is exposed as a usable
master secret. A deployment keeps the two apart by domain separation, a
specification detail beyond our scope.

\begin{figure}[t]
\centering
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[node distance=6mm and 10mm]
  \node[gwevent] (sig) {$\sigma$};
  \node[gwstate, right=of sig] (o0) {$o_0$};
  \node[gwtask, right=of o0] (st0)
     {$K_{0} := \Hcheap(o_{0} \,\|\, \Sh_{0})$;\\[2pt]
      $u_0 := \Hcheap(o_0 \,\|\, \Sh_0)$;\\[2pt]
      \textcolor{graytext}{\footnotesize wipe} $\{o_0, \Sh_0\}$;\\[2pt]
      $o_1 := \Hhard(u_0)$;};
  \node[gwstate, right=of st0] (o1) {$o_1$};
  \node[right=8mm of o1] (dots) {$\cdots$};
  \node[gwstate, right=8mm of dots] (oNm) {$o_{N-1}$};
  \node[gwtask, right=of oNm] (stNm)
     {$K_{N-1} := \Hcheap(o_{N-1} \,\|\, \Sh_{N-1})$;\\[2pt]
      $u_{N-1} := \Hcheap(o_{N-1} \,\|\, \Sh_{N-1})$;\\[2pt]
      \textcolor{graytext}{\footnotesize wipe} $\{o_{N-1}, \Sh_{N-1}\}$;\\[2pt]
      $o_N := \Hhard(u_{N-1})$;};
  \node[gwstate, right=8mm of stNm] (oN) {$o_{N}$};
  \node[gwtask, right=of oN] (stN)
     {$K_N := \Hcheap(o_{N} \,\|\, \Sh_{N})$};
  \node[gwstate, below=of st0] (K0) {$K_0$};
  \node[gwstate, below=of stNm] (KNm) {$K_{N-1}$};
  \node[gwstate, below=of stN] (KN) {$K_N$};
  \draw[gwflow] (sig) -- node[gwlabel, above]{$\Hcheap$} (o0);
  \draw[gwflow] (o0)  -- (st0);
  \draw[gwflow] (st0) -- node[gwlabel, above]{$\Hhard$} (o1);
  \draw[gwflow] (o1)  -- (dots);
  \draw[gwflow] (dots)-- node[gwlabel, above]{$\Hhard$} (oNm);
  \draw[gwflow] (oNm) -- (stNm);
  \draw[gwflow] (stNm)-- node[gwlabel, above]{$\Hhard$} (oN);
  \draw[gwflow] (oN) -- (stN);
  \draw[gwflow] (st0) -- node[gwlabel, right]{$\Hcheap$} (K0);
  \draw[gwflow] (stNm) -- node[gwlabel, right]{$\Hcheap$} (KNm);
  \draw[gwflow] (stN) -- node[gwlabel, right]{$\Hcheap$} (KN);
  \node[gwtask, above=9mm of st0] (sh0)
     {$\Sh_0$\\[1pt]\textcolor{graytext}{\footnotesize any $r_0$ of $p_{0,j}$}};
  \node[gwtask, above=9mm of stNm] (shNm)
     {$\Sh_{N-1}$\\[1pt]\textcolor{graytext}{\footnotesize any $r_{N-1}$ of $p_{N-1,j}$}};
  \node[gwtask, above=9mm of stN] (shN)
     {$\Sh_{N}$\\[1pt]\textcolor{graytext}{\footnotesize any $r_{N}$ of $p_{N,j}$}};
  \draw[gwflow] (sh0) -- (st0);
  \draw[gwflow] (shNm) -- (stNm);
  \draw[gwflow] (shN) -- (stN);
  \node[gwstate] (th0)  at (o0  |- sh0)  {$\{\theta_{0,j}\}$};
  \node[gwstate] (thNm) at (oNm |- shNm) {$\{\theta_{N-1,j}\}$};
  \node[gwstate] (thN)  at (oN  |- shN)  {$\{\theta_{N,j}\}$};
  \draw[gwflow] (o0)  -- node[gwlabel, right]{$\Hcheap$} (th0);
  \draw[gwflow] (oNm) -- node[gwlabel, right]{$\Hcheap$} (thNm);
  \draw[gwflow] (oN)  -- node[gwlabel, right]{$\Hcheap$} (thN);
  \draw[gwflow] (th0)  -- (sh0);
  \draw[gwflow] (thNm) -- (shNm);
  \draw[gwflow] (thN)  -- (shN);
\end{tikzpicture}}
\caption{\textbf{The TGPO orbit} (\S\ref{sec:gw}). A public,
precomputation-resistant timechain salt $\sigma$ (the Namtso primitive) seeds a
chain of $N$ memory-hard stages. At each stage the raw inputs
$o_{i-1}\,\|\,\Sh_{i-1}$ are folded by the \emph{cheap} inner hash $\Hcheap$ and
\emph{wiped} before the long memory-hard step $\Hhard$, so seizable material
exists only for an instant --- shrinking the window in which $o_{i-1}, \Sh_{i-1}$ are
reachable. Each board $o_i$ derives the fractal parameters
$\theta_{i,j} = \Hcheap(o_i \| j)$ on which its points $p_{i,j}$ are recognized; any
$r_i$ of those points reconstruct the whole Shamir polynomial $\Sh_i$, absorbed into
the \emph{next} orbit link, so no single point is checkable in isolation. The terminal secrets $K_i =
\Hcheap(o_i \,\|\, \Sh_i)$ deliberately use the cheap hash, keeping the final window
instant. By construction, coercion resistance happens for $i \geq 1$.}
\label{fig:orbit}
\end{figure}

\subsection{No single-point oracle}

Each stage $i$ carries not an individual point but a \emph{whole Shamir
polynomial}~\cite{shamir1979}. Stage $i$ has $s_i$ points $p_{i,j}$, each a
32-bit leaf-area of a fractal $\theta_{i,j} = \Hcheap(o_i \| j)$; any $r_i$ of
them reconstruct the degree-$(r_i{-}1)$ polynomial $\Sh_i$ of $r_i \cdot 32 \ge
64$ bits ($r_i \ge 2$). The orbit absorbs the \emph{full} polynomial $\Sh_i$,
not its constant term $f(0)$.

\begin{remark}[Block-orbit $r \ge 2$ condition]
Because the smallest object any orbit link commits is a full stage ($\ge 64$
bits), no individual point $p_{i,j}$ is ever checkable in isolation --- there is
no sub-threshold oracle against which a single guessed point could be verified.
This is the block-orbit $r \ge 2$ condition, realized as Shamir $r_i \ge 2$ per
stage.
\end{remark}

\subsection{Tacit multi-fractal stages}

The points $p_{i,j}$ instantiate Assumption~\ref{ass:tkba}: they are
recognizable on their fractal boards but not transmissible without
$\theta_{i,j}$ (TKBA$_1$), and the deep $\theta_{i,j}$ are regenerated from
$o_i$ --- which itself requires walking the memory-hard chain (TKBA$_2$). Using
several shallow-zoom fractals per stage lets a stage carry $r_i \cdot 32$ bits
at low zoom depth per board, keeping each point recognizable while tuning stage
entropy in 32-bit steps.

\subsection{Cheap terminal secret}

The coercion-resistant master secrets are all
\begin{equation}
  K_i, \qquad 1 \le i,
  \label{eq:master}
\end{equation}
deliberately using the \emph{cheap} $K_i = \Hcheap(o_i \,\|\, \Sh_i)$.

Each $K_i$ ($i \ge 1$) is a full instantiation of the abstract master secret $K$
that \S\ref{sec:chain} reasons about: the orbit yields not one secret but a nested
\emph{family} of master secrets, and every $K$-result --- the floor
(Theorem~\ref{thm:floor}), the deadly-race analysis --- holds of each. $K_0$ is set
aside: stage~$0$'s board $o_0$ derives from the public salt alone
(\eqref{eq:orbit}), so it sits below the memory-hard chain that gives the deeper
stages their floor.

A memory-hard last
step would only \emph{prolong} the window (\S\ref{sec:residual-seizure}) in which $o_N$ and the final points are 
live (paying an $\Hhard$ \emph{after} the last point is recognized), worsening the 
very window we shrink in~\eqref{eq:orbit}. The resistance therefore lives in 
\emph{entropy}: standard deep stages carry 96 bits ($r_i = 3$), so a cheap ledger 
brute of $\Sh_N$ from a bare $o_N$ costs $2^{96}$ --- infeasible by~\ref{s:infeasiblec} --- while the
terminal window stays instant.

\subsection{The floor}

\begin{theorem}[The floor on the master secret]\label{thm:floor}
Under Assumptions~\ref{ass:power}--\ref{ass:tkba} and the standard build of
\eqref{eq:orbit}--\eqref{eq:master}, from every seizable state \emph{save a single
residual window} (\S\ref{sec:residual-seizure}) a target master secret $K_N$ is
\emph{prohibitive} to reach --- its cost meets the floor
(Stipulation~\ref{ass:feas}). Consequently a device seizure outside that window
yields nothing feasible --- a \emph{clear attacker failure} in the sense of
Criterion~\ref{prin:nga}, with no racer for $\Attacker$ to reach.
\end{theorem}

\begin{proof}[Proof by case analysis over seizable states]
From a seized $o_i$ ($i < N$), reaching $K_N$ requires guessing
$\Sh_i, \dots, \Sh_N$; each $\Sh_l$ guess is $2^{r_l \cdot 32}$ and is
$\Hhard$-gated, since it is checked only by recomputing the memory-hard link
\eqref{eq:orbit}. Preimage resistance of $\Hcheap, \Hhard$ makes the orbit
forward-only: a seized $o_i$ cannot yield $o_{i-1}$. We enumerate:
\begin{itemize}[nosep,leftmargin=1.4em]
  \item \emph{Pure device seizure} (no coercion; only time-lock-gated~\cite{rsw1996}
        blobs at rest). All tacit points are required; $K$ is unreachable.
  \item \emph{Wrench of stage~0} ($p_{0,\cdot}$, always present since $\sigma$ is
        public). $\Attacker$ computes $o_1$ with one $\Hhard$; from $o_1$, $K_N$
        costs $2^{\sum_{j\ge 1} r_j\cdot 32}$, which is $2^{96}$ or more in the
        recommended standard builds~\cite{gw-design}, each guess $\Hhard$-gated ---
        prohibitive.
  \item \emph{Mid-orbit seizure} at $o_i$ ($0 < i < N$). $K_N$ costs $\ge 2^{96}$
        cheap and is $\Hhard$-gated per guess --- prohibitive.
  \item \emph{Residual} $o_N$ present. Treated separately in
        \S\ref{sec:residual-seizure}.
\end{itemize}
Every case except the residual leaves $K_N$ at the floor
(Stipulation~\ref{ass:feas}).
\end{proof}

\subsection{The tolerated residual seizure window}
\label{sec:residual-seizure}

One sliver escapes the floor, and it is first a \emph{seizability} gap --- not yet a
deadly race. It is the lone exception of Theorem~\ref{thm:floor}: a wrench that lands
with the final board $o_N$ imminently or currently live, and subdues $\Victim$ before
the wipe (\eqref{eq:orbit}), catches the derivation essentially complete and $\Victim$
under control. In that coincidence $\Attacker$ \emph{does} reach $K$ and the stash is
lost --- we concede it plainly. The floor is a claim about \emph{seizability}, and
precisely here it fails; what keeps the failure a mere \emph{residual} is how narrow
the coincidence is --- a precise landing on the brief live-$o_N$ interval, and a
subdual before any wipe or reset.

\subsection{The tolerated residual deadly-race window}
\label{sec:residual-dr}

Funds-loss, though, is a \emph{separate} axis from the \emph{deadly race}, and it is
the latter this section turns on: does the same window also manufacture an incentive
to \emph{kill} $\Victim$? That does \emph{not} follow from the seizure. Killing buys
$\Attacker$ only a \emph{shaving} of the final step --- after the
\emph{second-to-last} point of stage $N$ is surrendered, a cheap
$2^{32}\cdot\Hcheap$ brute (\eqref{eq:master} is cheap) reaches $K$ in
${\approx}1$~minute, versus waiting for a cooperating coerced $\Victim$ to recollect
it. Whether that shaved minute pays an assassination takes \emph{further} conditions,
which we test against the priced adversary $\mathrm{WDY}[W,c]$
(Definition~\ref{def:priced}), the model appropriate to a quantitative window ---
against the only thing that matters: the kill condition of Lemma~\ref{lem:drl},
$(1 - p_A)\,W > c$. We argue it is, more likely than not, unmet.

Two events govern the marginal value of killing $\Victim$ in this window:
\begin{itemize}[nosep,leftmargin=1.4em]
  \item $\mathsf{Corr}$ --- \emph{the points $\Victim$ has surrendered so far are
        correct}; and
  \item $\mathsf{Esc}$ --- \emph{the ${\approx}1$--$2$ minutes shaved by
        brute-forcing the last one or two points, rather than waiting for a
        cooperating coerced $\Victim$ to recollect them, make the difference
        between a successful escape from the crime scene and not}.
\end{itemize}
Killing can raise $p_A$ only inside $\mathsf{Corr}\cap\mathsf{Esc}$: outside
$\mathsf{Esc}$ the shaved minutes change no outcome, and outside $\mathsf{Corr}$
(below) killing \emph{lowers} $p_A$. The five grounds below --- grouped by which
term of $(1 - p_A)\,W > c$ they act on --- show the inequality fails.

\smallskip
\noindent\emph{Conditional on $\mathsf{Corr}$, the gain $(1 - p_A)\,W$ is minimal
($p_A$ is already ${\approx}\,1$):}
\begin{enumerate}[nosep,leftmargin=1.6em]
  \item a well-trained fractal is recognized in ${\approx}1$ minute, so
        brute-forcing the last point saves $\Attacker$ at most that
        ${\approx}1$--$2$ minutes over coercing it --- bounding the entire
        interval on which $\mathsf{Esc}$, and hence any gain from killing, can
        act;
  \item $\Attacker$'s plan already budgets time-lock or re-derivation, subdue, and
        interface time, so $\Pr[\mathsf{Esc}]$ is small: the residual minute
        rarely flips the escape, and killing pays off only inside $\mathsf{Esc}$;
  \item the terminal $K$ is deliberately cheap (\eqref{eq:master} keeps
        memory-hardness in the orbit, not the terminal step), so $\Attacker$ can
        \emph{pre-stage} the $2^{32}$ brute as a ``victim-stalls'' contingency ---
        recovering the shaved minutes \emph{without} killing, and draining the
        gain to ${\approx}\,0$.
\end{enumerate}

\noindent\emph{Absent $\mathsf{Corr}$, killing makes $p_A$ \textbf{fall}, not
rise:}
\begin{enumerate}[nosep,leftmargin=1.6em,start=4]
  \item if any surrendered point is wrong, $\Victim$ is $\Attacker$'s only route
        to a corrected one; eliminating $\Victim$ burns the coercion retry and
        collapses $p_A$ toward $0$. Since $\Attacker$ cannot verify
        $\mathsf{Corr}$ before broadcasting, the \emph{expected} change in $p_A$
        from killing is dragged below its $\mathsf{Corr}$-only value --- and can
        turn negative.
\end{enumerate}

\noindent\emph{And the cost $c$ is large:}
\begin{enumerate}[nosep,leftmargin=1.6em,start=5]
  \item the killing sharply \emph{worsens judicial liability} --- murder
        aggravated by frivolous motive \emph{and} by the victim's defenselessness,
        atop armed robbery --- so $c$ sits well above the minute-scale
        $(1 - p_A)\,W$ the first four grounds leave on the table.
\end{enumerate}

Whether the window opens after the $(r_N{-}1)$-th or $(r_N{-}2)$-th point rests
on the softest number of Stipulation~\ref{ass:feas} --- inside the tolerated
reasoning either way.

\medskip
\noindent\textbf{Net.} The relevant quantity is \emph{not} $(1 - p_A)\,W$, which
is non-negative by definition ($p_A \in [0,1]$), but the \emph{utility increment}
of the assassinate-then-brute strategy over keeping the victim cooperating.
Writing $\Delta p_A$ for the change in $\Attacker$'s win probability that strategy
induces, it is rational only if $\Delta p_A\,W > c$, and
\[
  \Delta p_A \;=\;
  \underbrace{\Pr[\mathsf{Corr}\cap\mathsf{Esc}]}_{\text{gain (grounds 1--3): minimal}}
  \;-\;
  \underbrace{\Pr[\neg\mathsf{Corr}]\cdot q}_{\text{loss (ground 4): burned retry}},
\]
where $q \in [0,1]$ is the win probability a still-cooperating victim would
restore --- via a corrected point --- and that killing forfeits. The gain term is
small ($\mathsf{Esc}$ is unlikely, is realized only within $\mathsf{Corr}$, and
even then is bounded to a minute the brute can be pre-staged around); the loss
term is a strict subtraction growing with $\Pr[\neg\mathsf{Corr}]$; and $c$ is
large (ground 5). Hence the criterion the strategy must satisfy,
$\Delta p_A\,W - c > 0$, is false with overwhelming probability, so the kill
strategy is --- much more likely than not --- \emph{not} rationally advantageous.

\smallskip
\noindent In plain English, the residual deadly-race window lives only in the
intersection of a wrench attacker who:
\begin{enumerate}[nosep,leftmargin=1.9em]
  \item is \textbf{technically sophisticated} --- able to mount the $2^{32}$ brute
        and drive the interface. \emph{(Extrinsic to TGPO: granted to $\Attacker$
        by Kerckhoffs (Assumption~\ref{ass:kerckhoffs}), which already hands over
        the full protocol.)}
  \item \textbf{landed the attack inside the $o_N$-live window} --- timed
        precisely enough to catch stage $N$ available, or resourced enough to
        sustain coercion until $o_N$ was made available;
  \item \textbf{subdued $\Victim$ before any reset} of the derivation or the TLP;
  \item \textbf{judged, right after the second-to-last point, that ceasing the
        attack immediately was critical to escape} ($\mathsf{Esc}$) --- despite
        already having budgeted for a longer encounter (item~2);
  \item \textbf{could rule out every already-coerced point being incorrect}
        ($\mathsf{Corr}$); and
  \item \textbf{accepted the liability of a doubly-aggravated murder} --- frivolous
        motive \emph{and} victim defenselessness. \emph{(Once again extrinsic to
        TGPO: it burdens the deadly-racer attacker of any coercion-resistance
        protocol.)}
\end{enumerate}

\begin{remark}[Cloaking the window --- the Jade Clock]
The gain term carries a further hidden factor: the residual is reached only when
the attack \emph{coincides} with the brief interval in which $o_N$ is live. That
coincidence is itself suppressible. Anonymizing \emph{when} the vault-opening
window occurs --- the role of the outsourced anonymous time-lock (``Jade
Clock'')~\cite{gw-jadeclock} --- drives
$\Pr[\text{attack lands in the target } o_N\text{-live window}]$ down, and this factor
multiplies the already-minimal $\Pr[\mathsf{Corr}\cap\mathsf{Esc}]$. Here anonymity
of the \emph{timing} suppresses a residual that confidentiality of the \emph{secret}
alone does not reach.
\end{remark}

\begin{remark}[Design decision --- canonical-island highlighting]
Item~5 above (that $\Attacker$ cannot rule out $\neg\mathsf{Corr}$) can be
strengthened at the UX layer, to make an \emph{intentionally} wrong prior point
plausible. Whenever feasible the interface should keep the canonical-island
highlight active: this lets a coerced $\Victim$ perform a random zoom and then
feign a confident, plausible-looking selection of an \emph{incorrect} island.
Without the highlight the victim could not reliably produce a plausible selection
at all --- valid coordinates are a tiny fraction of the space, so an unaided pick
would most likely be rejected as invalid --- so it is the highlight that makes a
deliberately-wrong-yet-credible surrender available to the victim, and thus keeps
$\neg\mathsf{Corr}$ live in $\Attacker$'s belief (inflating the loss term of
$\Delta p_A$). A sophisticated $\Attacker$ could force a non-highlighting fork of
the app, but that costs further sophistication and wrench-time. This layer sits
\emph{on top of} a window of deadly-race vulnerability that is already
vanishingly unlikely (the six-way intersection above).
\end{remark}

\begin{remark}[Feigning is not load-bearing]
The $\neg\mathsf{Corr}$ loss term (ground~4) and its UX amplification (canonical-
island highlighting, above) only \emph{deepen} the case; they are not what carries
it. Grant $\Attacker$ the best of it --- $\Pr[\mathsf{Corr}] = 1$, an honest
$\Victim$ in flawless cooperation (\ref{d:subjugation}), with no feigning to fear. Then the loss
term vanishes and the kill increment collapses to its gain term alone,
\[
  \Delta p_A\,W - c \;=\; \Pr[\mathsf{Esc}]\,W - c,
\]
which grounds 1--3 already hold small ($\Pr[\mathsf{Esc}]$ tiny, the shaved
interval minute-scale and pre-stageable) against a large $c$ (ground~5). So the
residual is bounded on the \emph{gain} side by itself: feigning ($\neg\mathsf{Corr}$)
subtracts further and is a welcome bonus, but the window is already small without
it --- even against a perfectly honest, fully cooperating victim.
\end{remark}

\begin{remark}[Splitting a stash across several $K_i$]
Nothing forces a holder to route an entire stash through a single master secret; it
may be split across several $K_i$ --- distinct stages, or independent orbit setups
--- with two risk-management benefits, each diluting one of the residual failure
modes:
\begin{enumerate}[nosep,leftmargin=1.6em]
  \item \emph{Diluted seizure risk} --- the proverbial ``not all eggs in one
        basket.'' Should the residual \emph{seizure} window
        (\S\ref{sec:residual-seizure}), or any other failure mode of the
        construction, expose one $K_i$, only the fraction of the stash it guards is
        lost.
  \item \emph{Diluted deadly-race payoff.} In the residual \emph{deadly-race}
        window (\S\ref{sec:residual-dr}) the kill condition is $(1-p_A)\,W > c$;
        with the stash split, the $W$ at stake in any single window is only a
        fraction of the whole, lowering $\Attacker$'s assassination payoff and
        making the inequality harder to meet.
\end{enumerate}
\end{remark}

\subsection{Empirical grounding in the registry}
\label{sub:empirical}

The two stipulations that lean on the physical-attack registry~\cite{lopp-attacks}
--- the coercion-time budget $t$ (\S\ref{sec:limits}) and the murder-cost weighing of
this section --- admit directional empirical support. The registry records each
incident only as \emph{date, victim, location, headline}; it carries no duration or
outcome field, so we code the $342$ incident headlines (accessed 2026-07-19) by
keyword. The coding is coarse and the categories overlap; a reproducible script
accompanies the paper.\footnote{\texttt{registry-analysis/} in the source tree gives
the exact keyword patterns, per-year counts, and caveats.} Three things stand out.

\emph{The attack is frequent and worsening.} Recorded incidents climb from a handful
a year before 2017 to a peak of $82$ in 2025 --- the growth the introduction cites,
now counted rather than asserted.

\emph{The terminal move is real.} At least $5.3\%$ ($18/342$) of headlines record a
\emph{killed} or \emph{murdered} victim. A homicide is usually reported as a homicide,
not as a ``Bitcoin attack'', so this is a \emph{lower} bound --- yet even so it shows
the assassination outcome the Deadly-Race Lemma (Lemma~\ref{lem:drl}) predicts is
attested in practice, and that the cost $c$ is weighed against an action attackers
demonstrably take.

\emph{Short attacks dominate; the registry over-counts the dramatic.} Most wrench
attacks are \emph{hand-over-now} events --- a threat, an immediate transfer, minutes
on scene; the long, cinematic kidnapping is the exception. A media-sourced registry
inverts this, because a mutilation-kidnapping is news where a knifepoint mugging is
not, so the kidnap share coded below \emph{over}-states the long tail rather than
establishing it. That TKBA is realistically \emph{less} effective against a
long-duration attack --- where hours of pen-and-paper effort under coercion
\emph{might} walk a deep stage --- is granted, but it is \emph{speculative} pending
the field study of \S\ref{sec:limits}. What is \emph{not} speculative is that the
fielded alternatives fail; the next case makes that concrete.

\begin{center}\small
\begin{tabular}{@{}lrr@{}}
\toprule
\textbf{Signal (headline keyword coding)} & \textbf{Incidents} & \textbf{Share} \\
\midrule
Killed / murdered victim \emph{(a lower bound)} & $18$  & $5.3\%$  \\
Kidnap / hostage / ransom (long-hold)           & $133$ & $38.9\%$ \\
Armed robbery at gunpoint (short-hold)          & $93$  & $27.2\%$ \\
Home invasion / break-in / raid                 & $35$  & $10.2\%$ \\
Torture or physical violence                    & $78$  & $22.8\%$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent Categories overlap (a kidnapping may also be violent or fatal) and do not
sum to $100\%$; shares are of all $342$ incidents, and the modality labels are a
headline proxy, not a measured duration. The sample is media-reported and
survivorship-biased --- deterred, unreported, and silently-fatal cases are absent ---
so every figure is directional and the fatality share in particular is a floor.

\medskip\noindent\textbf{A case in point --- Balland.} The January 2025 abduction of
David Balland, a co-founder of the hardware-wallet maker Ledger~\cite{balland}, is
instructive precisely because it is an \emph{embarrassment to the self-custody creed}.
A professional champion of self-custody was seized from his home and mutilated --- a
finger severed to force payment --- and neither wealth nor prominence prevented it. He
was freed by an elite \emph{state} police unit, and the ransom --- paid not by Balland
but by an associate --- was clawed back largely because part of it moved in a
\emph{centralized} stablecoin whose issuer could freeze it. A self-custody pioneer
made whole by the state and by centralization: two mechanisms external to, and in
tension with, the creed. Only the issuer freeze is independently verifiable; the
remainder rests on the parties' accounts, according to which roughly $5\%$ was never recovered.
The case also indicts the delegated route (\ref{r:remotewinner}): an associate
\emph{did} pay, which is exactly the compliance clause~\ref{d:nodelegatecoerce}
assumes away --- a real instance of the indirect coercion,
routed through the victim's body to a third party who will not refuse. For a brief
hand-over-now robbery a remote delegate is unreachable in time and so seems to help;
but merely \emph{not carrying} the device --- leaving the wallet in a home vault ---
does the same, while for the long attack the delegate is not out of reach but is the
ransom channel itself. The lesson is not that Balland erred: it is that, against a
determined long-hold attacker, the fielded options collapse to state rescue and
centralized freezing, whereas the tacit route removes the leverage --- no standing
device, no hostage token, no delegate to pay --- rather than relying on ex-post
recovery.

