% ════════════════════════════════════════════════════════════════════════════
\section{Ethics and responsible disclosure}
\label{sec:ethics}
% ════════════════════════════════════════════════════════════════════════════

This is offensive-flavored security research with direct life-safety stakes: we
formally derive an \emph{assassination} incentive (Lemma~\ref{lem:drl}). We
therefore state plainly why publishing it is, on balance, protective.

\textbf{The incentive is disclosed, not created.} The Deadly Race is a property of a
situation a coercer already faces; naming it hands nothing to an attacker who, by
Kerckhoffs (Assumption~\ref{ass:kerckhoffs}), is already assumed to know the protocol
and the landscape. What publication changes is only that \emph{defenders} can now
measure a design against the bar (Criterion~\ref{prin:nga}) and reject the ones that
manufacture the incentive. We describe an incentive and the failure modes of existing
defenses --- not a targeting method, and no operational how-to; the paper's
constructive content is defensive.

\textbf{Obscurity is not a sound reason to withhold.} The alternative --- not
publishing analyses of attack vectors and the failure modes of deployed defenses ---
is itself a bet on obscurity, and both theory and data say that bet loses.
As Kerckhoffs' principle has held for a century, a defense that works only while the
adversary stays ignorant provides something worse than defenselessness: \emph{a false sense 
of security}. Empirically, the physical-attack registry~\cite{lopp-attacks} and the 
accompanying economic analysis~\cite{gw-justification} show exactly what the principle 
predicts --- wrench attacks are frequent and rising, and the community's entrenched counsel
(\emph{keep a low profile}, \emph{never disclose ownership}, \emph{deny if asked} ---
advice prominent channels actively promote, catalogued in~\cite{gw-justification})
has not stemmed them. Security knowledge diffuses to criminal actors regardless of
academic reticence; withholding it handicaps only the defenders who would otherwise
design against the very incentive we name. Publishing the Deadly Race, \emph{together
with} a bar that rejects the designs which create it, is net-protective of the
holders it concerns.

\textbf{Framing and restraint.} We keep the framing on protecting at-risk holders,
disclose our own bounded residual honestly (\S\ref{sec:residual-seizure}) rather than
overclaim, and treat the shipping alternatives we classify (\S\ref{sec:classify}) as
legitimate clearances by the other route --- not targets.
