\documentclass[a4paper,11pt]{article}

% ============================================================================
%  The Deadly Race — a formal wrench-attack threat model
%  First LaTeX manuscript. Source: papers/deadly-race-coercion-resistance.md,
%  great-wallet/THREAT_MODEL.md, next-steps/coercion-resistant-orbit-protocol.md
% ============================================================================

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=24mm]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{hyperref}

% ── Brand palette (shared with the Great Wall paper set) ───────────────────
\definecolor{accent}{HTML}{2F6F4E}
\definecolor{accentdark}{HTML}{234F38}
\definecolor{accentlight}{HTML}{EBF3EE}
\definecolor{darktext}{HTML}{1E1E1E}
\definecolor{graytext}{HTML}{646464}
\definecolor{attackcol}{HTML}{C0392B}

\hypersetup{colorlinks=true, linkcolor=accentdark, urlcolor=accentdark,
            citecolor=accentdark,
            pdftitle={The Deadly Race: a formal wrench-attack threat model},
            pdfauthor={Yuri da Silva Villas Boas}}

% ── Headers / footers ──────────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\small\textit{\color{graytext}The Deadly Race}}
\fancyfoot[C]{\small\color{graytext}\thepage}
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[C]{\small\color{graytext}\thepage}}

% ── Section styling ────────────────────────────────────────────────────────
\titleformat{\section}{\large\bfseries\color{accent}}{\thesection}{0.7em}{}
  [\vspace{-0.5em}{\color{accent}\rule{\textwidth}{0.4pt}}]
\titleformat{\subsection}{\normalsize\bfseries\color{darktext}}{\thesubsection}{0.6em}{}

% ── Theorem environments ───────────────────────────────────────────────────
\newtheoremstyle{gw}{0.6em}{0.6em}{\itshape}{}{\bfseries\color{accentdark}}{.}{.5em}{}
\theoremstyle{gw}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{principle}{Principle}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

% ── Notation shorthands ────────────────────────────────────────────────────
\newcommand{\Hcheap}{\mathsf{H}}
\newcommand{\Hhard}{\mathsf{H}^{\!*}}
\newcommand{\Sh}{\mathit{Sh}}
\newcommand{\TLP}{\mathsf{TLP}}
\newcommand{\sftstar}{64^{*}}
\newcommand{\Victim}{\mathcal{V}}
\newcommand{\Attacker}{\mathcal{A}}

\begin{document}

% ════════════════════════════════════════════════════════════════════════════
% TITLE
% ════════════════════════════════════════════════════════════════════════════
\thispagestyle{plain}
\begin{center}
{\fontsize{22}{26}\selectfont\bfseries\color{accent}The Deadly Race}\\[8pt]
{\large A Formal Threat Model for Physical-Coercion (``Wrench'') Attacks,\\
 and a Construction that Clears It}\\[12pt]
{\color{accent}\rule{78mm}{0.5pt}}\\[9pt]
{\itshape\color{graytext}Great Wall coercion-resistance paper series}\\[4pt]
{\small\color{graytext}Yuri da Silva Villas Boas \textperiodcentered{} First manuscript, July 2026}
\end{center}

\vspace{6pt}

\begin{abstract}
\noindent Physical-coercion (``wrench'') attacks defeat custody schemes that
key management and cryptography treat as out of scope. We give a \emph{formal
model} of coercion against a secret-holder and prove that a large class of
``graceful'' recovery designs --- those that leave a device seizure holding a
\emph{feasible-but-slower} path to the secret --- are strictly worse than
useless: they manufacture a material incentive to \emph{assassinate} the
victim. We name this the \textbf{Deadly Race}, derive it from a single
impossibility (one cannot prove one has forgotten), and distil a design bar ---
the \textbf{No-Gray-Area Principle} --- that any coercion-resistant scheme must
clear. We then present a construction, \textbf{Great Wall}, that clears the bar
for the Bitcoin self-custody setting while keeping custody \emph{individual},
and we locate a shipping alternative --- timelock-rescue vaults --- precisely:
it clears the same bar by the \emph{other} available route, at the cost of a
trusted third party. The framework fixes a bar; it does not claim Great Wall is
the unique construction that clears it.
\end{abstract}

\vspace{4pt}

% ════════════════════════════════════════════════════════════════════════════
\section{Introduction}
% ════════════════════════════════════════════════════════════════════════════

Coercion is the unmodeled attack. Standard threat models --- Dolev--Yao on the
wire~\cite{dolev-yao}, \textsc{ind-cca} for encryption, forward secrecy for
sessions --- all assume the adversary cannot compel the \emph{holder} of a
secret. For bearer assets that assumption is empirically false: the physical
attack registry maintained by Lopp~\cite{lopp-attacks}, and the systematic
study of the phenomenon in the financial-technologies literature~\cite{aft-wrench},
document a growing series of incidents in which a Bitcoin holder is physically
threatened with a ``\$5 wrench'' until they surrender their keys.

Cryptographic hardness does not help here. A wrench attacker does not break the
cipher; they compel the person who can operate it. Worse, the standard defence
offered to holders --- \emph{obscurity} (``never tell anyone you own
Bitcoin'') --- is not a security mechanism at all in the sense of
Kerckhoffs~\cite{kerckhoffs1883}: it is a bet that the attacker lacks knowledge
the defender has, and it degrades precisely as adoption spreads that knowledge.

This paper models coercion directly. Our contributions are:

\begin{enumerate}[nosep,leftmargin=1.6em]
  \item a \textbf{formal coercion model} (\S\ref{sec:model}) with an explicit
        adversary, a Kerckhoffs premise, and an engineering ``feasibility
        line'' that turns asymptotic security into concrete parameter bounds;
  \item the \textbf{Deadly-Race impossibility chain} (\S\ref{sec:chain}): a
        classical impossibility (you cannot prove you forgot) that escalates,
        step by step, into an incentive to murder the victim;
  \item the \textbf{No-Gray-Area Principle} (\S\ref{sec:chain}), the design bar
        that a coercion-resistant scheme must clear, together with a
        \emph{reachability} dichotomy that classifies every clearance route;
  \item a \textbf{construction} (\S\ref{sec:gw}), the Great Wall orbit, that
        meets the bar with individual custody, including a proof that the master
        secret is at least $\sftstar$ from every seizable state; and
  \item a \textbf{taxonomy} (\S\ref{sec:classify}) that classifies existing
        designs by \emph{which} clearance route they take --- illustrated on
        shipping timelock-rescue vaults.
\end{enumerate}

For citation, we name the central results after their first statement in the
Great Wall design record~\cite{gw-threatmodel}: the \textbf{Deadly-Race Lemma}
(\emph{Villas Boas' Lemma}) and the \textbf{No-Gray-Area Principle}
(\emph{Villas Boas' Principle}).

% ════════════════════════════════════════════════════════════════════════════
\section{Model}
\label{sec:model}
% ════════════════════════════════════════════════════════════════════════════

\subsection{Principals and capabilities}

\begin{definition}[Principals]
The \textbf{holder} $\Victim$ possesses (in memory and on devices) whatever is
needed to reach a master secret $K$ that gates an asset. The \textbf{coercer}
$\Attacker$ seeks $K$. Optional \textbf{heirs} or \textbf{delegates} may hold
partial capability on $\Victim$'s behalf.
\end{definition}

\begin{assumption}[Kerckhoffs, premise~0]\label{ass:kerckhoffs}
$\Attacker$ knows the protocol in full: all algorithms, all source, $\Victim$'s
setup topology, and every in-scope parameter. Only the protocol \emph{secrets}
are hidden. Every result below is proved \emph{against} such an $\Attacker$;
security by obscurity is assumed to contribute nothing.
\end{assumption}

\begin{assumption}[Adversary power]\label{ass:power}
$\Attacker$ is Dolev--Yao on the wire~\cite{dolev-yao}: it observes all
transmitted plaintext and ciphertext but cannot decrypt beyond its
computational budget. $\Attacker$ may \emph{seize any device} and read all
state on it (vault blobs, time-lock blobs, commitment scripts, review
schedules). $\Attacker$ has \emph{unbounded compute within a wall-clock custody
window}, and may \emph{physically coerce} $\Victim$ for a bounded duration ---
bounds calibrated against the incident durations in the registry~\cite{lopp-attacks}.
\end{assumption}

\subsection{The feasibility line}

Asymptotic ``hard'' and ``easy'' are useless against a fixed, resourced
attacker; we replace them with two engineering stipulations that fix what
\emph{feasible} means and turn the lemmas into concrete bounds.

\begin{assumption}[Feasibility stipulations]\label{ass:feas}
Let a \emph{cheap} evaluation be one call to a non-memory-hard hash $\Hcheap$,
and a \emph{memory-hard} evaluation one call to an hours-scale Argon2d-class
function $\Hhard$~\cite{argon2}.
\begin{itemize}[nosep,leftmargin=1.4em]
  \item \textbf{S1 (feasible).} $2^{32}$ cheap evaluations are within
        $\Attacker$'s budget.
  \item \textbf{S2 (infeasible).} $2^{64}$ memory-hard evaluations --- written
        $\mathbf{64^{*}}$ --- are beyond it.
\end{itemize}
\end{assumption}

Two currencies span the gap between them. \emph{Entropy} buys $32 \to 64$: a
second independent 32-bit stage. But plain $2^{64}$ \emph{cheap} work still sits
at the border of a resourced attacker's reach (hours), so the $64 \to \sftstar$
step must be bought by \emph{memory-hardness} --- which is why the gating
function has to be Argon2-class. We refer to plain cheap $2^{64}$ throughout as
the \emph{softest number}: it must be named explicitly wherever it is invoked,
never silently treated as infeasible.

\subsection{The tacit-knowledge premise}

The construction of \S\ref{sec:gw} rests the secret on \emph{tacit} knowledge.
We state the premise abstractly here; \S\ref{sec:gw} instantiates it.

\begin{assumption}[Tacit knowledge, TKBA]\label{ass:tkba}
The secret is a set of fractal locations that are \emph{recognisable but not
transmissible}.
\begin{itemize}[nosep,leftmargin=1.4em]
  \item \textbf{TKBA$_1$.} A point is intransmissible without the fractal
        parameters that render it; $\Victim$ cannot dictate it in the abstract.
  \item \textbf{TKBA$_2$.} The \emph{deep} fractal parameters are not a
        hand-overable artifact; producing them requires walking a memory-hard
        chain that later locations do not exist before.
\end{itemize}
\end{assumption}

% ════════════════════════════════════════════════════════════════════════════
\section{The Deadly-Race impossibility chain}
\label{sec:chain}
% ════════════════════════════════════════════════════════════════════════════

The core results form an escalating chain: each follows from the one before,
starting from a classical impossibility and ending in a design bar.

\begin{lemma}[Non-Negative-Proof Lemma, NNPL]\label{lem:nnpl}
No agent can furnish satisfactorily verifiable proof of \emph{lack of access} to
a given piece of information --- whether that access would be through their own
memory, or directly or indirectly through physical media. One can prove one
\emph{knows} something; one cannot prove one has \emph{forgotten} it, nor that
no backup of it exists anywhere.
\end{lemma}

\begin{proof}[Argument]
Knowledge admits a positive certificate: exhibit the datum, or answer a
challenge that only a knower could answer. Non-knowledge admits no such
certificate. Any protocol in which $\Victim$ demonstrates ignorance is one in
which a knowing $\Victim$ could simulate the same transcript by withholding what
they know; and no observation of $\Victim$ or of any finite set of media
excludes the existence of a further, unobserved copy. The asymmetry is
information-theoretic, not a matter of effort.
\end{proof}

\begin{lemma}[Deadly-Race Lemma / Villas Boas' Lemma]\label{lem:drl}
Because a released $\Victim$ cannot prove (Lemma~\ref{lem:nnpl}) that they retain
no resumable copy of their protocol state, any seizure that leaves $\Attacker$
with enough information to \emph{eventually} reach $K$ --- however much slower
than legitimate use --- defines a \textbf{race} between $\Attacker$ (working
from the seized information) and the released $\Victim$ (presumed to hold
complete information). Whoever reaches $K$ first seizes whatever it gates. The
existence of that race creates a \textbf{material incentive for $\Attacker$ to
assassinate $\Victim$} --- and possibly the heirs --- upon seizing sufficient
information, so as to eliminate the competing racer.
\end{lemma}

\begin{proof}
Suppose the seizure leaves $\Attacker$ on a feasible path to $K$ of wall-clock
length $T_A$, and $\Victim$, once released, on a path of length $T_V \le T_A$.
By Lemma~\ref{lem:nnpl}, $\Attacker$ cannot verify any promise by $\Victim$ to
abstain or to have destroyed their copy, so $\Attacker$ must assume $\Victim$
races. Eliminating $\Victim$ deletes the competing racer and converts an
uncertain win into a certain one; it is therefore a strictly dominant action
for a payoff-maximising $\Attacker$ whenever the marginal cost of the killing is
below the contested value. The incentive is a structural consequence of the
race, independent of $\Attacker$'s temperament.
\end{proof}

\begin{principle}[No-Gray-Area Principle / Villas Boas' Principle]\label{prin:nga}
A coercion-resistant protocol must, for a fixed threat model, admit \textbf{only}
outcomes in which a wrench attack \emph{clearly succeeds} or \emph{clearly
fails} --- never a race. A protocol in which some wrench-attack outcome is a
race is, by construction, not acceptable: the gray area is precisely where the
assassination incentive of Lemma~\ref{lem:drl} lives.
\end{principle}

\begin{proof}[Operational restatement]
Seizing a device must yield either \emph{nothing feasible} (clear failure) or
\emph{the secret itself while $\Attacker$ is present and $\Victim$ is captive}
(clear success, no free racer) --- never a feasible-but-slower offline path that
$\Attacker$ could pursue after releasing or killing $\Victim$. ``Feasible'' is
judged against the attacker of Assumptions~\ref{ass:power}--\ref{ass:feas}, not
against a casual one.
\end{proof}

\begin{remark}[Reachability --- the remote-racer escape]\label{rem:reach}
The assassination incentive of Lemma~\ref{lem:drl} is realizable \emph{only
against a racer $\Attacker$ can reach}. A racer beyond physical reach --- e.g.\
a \emph{remote} rescuer or delegate --- cannot be eliminated, so their racing
advantage stands and the attack fails cleanly. Remoteness of the racer is
therefore itself a remediation. Hence there are exactly \textbf{two honest ways
to clear Principle~\ref{prin:nga}}:
\begin{enumerate}[nosep,leftmargin=1.6em]
  \item \textbf{remove the race} --- admit no feasible seizure path at all
        (custody stays individual); or
  \item \textbf{remove $\Attacker$'s reach over the racer} --- interpose a
        remote delegate (custody becomes shared).
\end{enumerate}
This dichotomy is the classification axis of \S\ref{sec:classify}. The escape
buys safety by moving the winning racer \emph{off the individual} --- it
requires a trusted third party.
\end{remark}

% ════════════════════════════════════════════════════════════════════════════
\section{Construction --- Great Wall (clears by removing the race)}
\label{sec:gw}
% ════════════════════════════════════════════════════════════════════════════

We now exhibit a construction that clears Principle~\ref{prin:nga} by the first
route of Remark~\ref{rem:reach}: it admits \emph{no feasible seizure path}, so
custody remains individual. Full normative detail is in the canonical
spec~\cite{gw-orbit}; we give the parts the theorem needs.

\subsection{The orbit}

Let $\Hcheap$ be a cheap, entropy-preserving one-way hash and $\Hhard$ an
memory-hard (Argon2-class) hash of tunable cost. Let $\sigma$ be a public,
precomputation-resistant \emph{timechain salt} whose cross-user amortization is
negligible (the companion Namtso primitive~\cite{gw-timechain-salt}). Define an
\textbf{orbit} of $N$ deep stages:
\begin{align}
  o_0 &= \Hcheap(\sigma), \\
  o_i &= \Hhard\!\big(\, \Hcheap(o_{i-1} \,\|\, \Sh_{i-1}) \,\big),
         \qquad 1 \le i \le N,
  \label{eq:orbit}
\end{align}
where the raw inputs $\{o_{i-1}, \Sh_{i-1}\}$ are \textbf{wiped} in the instant
between the cheap inner hash and the long memory-hard step. Computing
$c := \Hcheap(o_{i-1}\|\Sh_{i-1})$ first (instant), wiping, then running the
long $o_i := \Hhard(c)$, means the raw prior orbit point and Shamir secret exist
only momentarily --- not across the whole memory-hard window. This directly
shrinks the window in which $K$ is seizable, and is the reason not to write
$\Hhard(o_{i-1}\|\Sh_{i-1})$ directly.

\subsection{No single-point oracle}

Each stage $i$ carries not an individual point but a \emph{whole Shamir
polynomial}~\cite{shamir1979}. Stage $i$ has $s_i$ points $p_{i,j}$, each a
32-bit leaf-area of a fractal $\theta_{i,j} = \Hcheap(o_i \| j)$; any $t_i$ of
them reconstruct the degree-$(t_i{-}1)$ polynomial $\Sh_i$ of $t_i \cdot 32 \ge
64$ bits ($t_i \ge 2$). The orbit absorbs the \emph{full} polynomial $\Sh_i$,
not its constant term $f(0)$.

\begin{remark}[Block-orbit $k \ge 2$ condition]
Because the smallest object any orbit link commits is a full stage ($\ge 64$
bits), no individual point $p_{i,j}$ is ever checkable in isolation --- there is
no sub-threshold oracle against which a single guessed point could be verified.
This is the block-orbit $k \ge 2$ condition, realised as Shamir $t_i \ge 2$ per
stage.
\end{remark}

\subsection{Tacit multi-fractal stages}

The points $p_{i,j}$ instantiate Assumption~\ref{ass:tkba}: they are
recognisable on their fractal boards but not transmissible without
$\theta_{i,j}$ (TKBA$_1$), and the deep $\theta_{i,j}$ are regenerated from
$o_i$ --- which itself requires walking the memory-hard chain (TKBA$_2$). Using
several shallow-zoom fractals per stage lets a stage carry $t_i \cdot 32$ bits
at low zoom depth per board, keeping each point recognisable while tuning stage
entropy in 32-bit steps.

\subsection{Cheap terminal secret}

The master secret is
\begin{equation}
  K = \Hcheap(o_N \,\|\, \Sh_N),
  \label{eq:master}
\end{equation}
deliberately using the \emph{cheap} $\Hcheap$. A memory-hard last step would only
\emph{prolong} the window in which $o_N$ and the final points are live (paying an
$\Hhard$ \emph{after} the last point is recognised), worsening the very window
we shrink in~\eqref{eq:orbit}. The resistance therefore lives in \emph{entropy}:
standard deep stages carry 96 bits ($t_i = 3$), so a cheap ledger brute of
$\Sh_N$ from a bare $o_N$ costs $2^{96}$ --- infeasible --- while the terminal
window stays instant.

\subsection{The $\sftstar$ floor}

\begin{theorem}[$\sftstar$ floor on the master secret]\label{thm:floor}
Under Assumptions~\ref{ass:power}--\ref{ass:tkba} and the standard build of
\eqref{eq:orbit}--\eqref{eq:master}, from every seizable state the master secret
$K$ is at least $\sftstar$ away: no single seizure leaves $K$ fewer than two
memory-hard 32-bit stages from reach. Consequently a device seizure yields
nothing feasible --- a \emph{clear failure} in the sense of
Principle~\ref{prin:nga}, with no racer for $\Attacker$ to reach.
\end{theorem}

\begin{proof}[Proof by case analysis over seizable states]
From a seized $o_i$ ($i \le N$), reaching $K$ requires guessing
$\Sh_i, \dots, \Sh_N$; each $\Sh_j$ guess is $2^{t_j \cdot 32}$ and is
$\Hhard$-gated, since it is checked only by recomputing the memory-hard link
\eqref{eq:orbit}. Preimage resistance of $\Hcheap, \Hhard$ makes the orbit
forward-only: a seized $o_i$ cannot yield $o_{i-1}$. We enumerate:
\begin{itemize}[nosep,leftmargin=1.4em]
  \item \emph{Pure device seizure} (no coercion; only time-lock-gated~\cite{rsw1996}
        blobs at rest). All tacit points are required; $K$ is unreachable.
  \item \emph{Wrench of stage~0} ($p_{0,\cdot}$, always present since $\sigma$ is
        public). $\Attacker$ computes $o_1$ with one $\Hhard$; from $o_1$, $K$
        costs $2^{\sum_{j\ge 1} t_j\cdot 32}$, which is $2^{96}$ or more in the
        standard ($N\ge 2$) build --- infeasible.
  \item \emph{Mid-orbit seizure} at $o_i$ ($i \le N$). $K$ costs $\ge 2^{96}$,
        each guess $\Hhard$-gated --- infeasible.
  \item \emph{Residual} $o_N$ present. Treated separately in
        \S\ref{sec:residual}.
\end{itemize}
Every case except the residual leaves $K \ge \sftstar$ --- two memory-hard
stages, beyond S2 of Assumption~\ref{ass:feas}.
\end{proof}

\begin{remark}[Why a last-stage KDF fails]
The floor is not automatic. In a naive sequential setup whose master secret is
$\mathrm{KDF}(p_N)$ --- determined by the \emph{last} stage alone --- a surprise
seizure at stage $N{-}1$ holds the preimage of stage $N$; deriving it and
brute-forcing the final 32-bit point costs $2^{32}$ (S1, feasible). That is a
feasible-but-slower path: a gray area, rejected by
Principle~\ref{prin:nga}. The requirement is that $K$ be $\ge \sftstar$ from
\emph{every} seizable state, which is exactly the no-single-point-oracle /
block-orbit ($k \ge 2$) condition met above.
\end{remark}

\subsection{The tolerated residual window}
\label{sec:residual}

One gray sliver survives: a wrench attack that lands with $o_N$
imminently or currently live can, after the \emph{second-to-last} point of stage
$N$ is surrendered, leave $\Attacker$ one cheap $2^{32}\cdot\Hcheap$ brute
(\eqref{eq:master} is cheap) --- roughly a one-minute window --- from $K$. We
report this honestly as a bounded residual rather than claim zero. It is
tolerated on five grounds:
\begin{enumerate}[nosep,leftmargin=1.6em]
  \item a well-trained fractal is recognised in $\sim$1 minute;
  \item $\Attacker$'s plan already budgets time-lock or re-derivation, subdue,
        and interface time --- a residual minute rarely changes the escape;
  \item assassinating \emph{trusts} that the earlier surrendered points were
        genuine; one wrong point and the coercion retry is burned;
  \item it sharply \emph{worsens judicial liability} --- murder qualified by
        futile motive \emph{and} by the victim's defenselessness, atop armed
        robbery; and
  \item the terminal $K$ is deliberately cheap (\S\ref{eq:master}), so keeping
        memory-hardness in the orbit rather than the terminal step removes any
        advantage $\Attacker$ would gain by pre-staging.
\end{enumerate}
Whether the window opens after the $(t_N{-}1)$-th or $(t_N{-}2)$-th point rests
on the softest number of Assumption~\ref{ass:feas} --- inside the tolerated
reasoning either way. Net: a tiny window in which $\Attacker$ is, more likely
than not, incentivised \emph{not} to act.

% ════════════════════════════════════════════════════════════════════════════
\section{Classification of existing designs}
\label{sec:classify}
% ════════════════════════════════════════════════════════════════════════════

Remark~\ref{rem:reach} gives a classification axis: a design that clears
Principle~\ref{prin:nga} does so either by \emph{removing the race} or by
\emph{removing $\Attacker$'s reach over the racer}. The framework should
classify a shipping design, and it does --- via the reachability remark, not by
calling it broken.

\subsection{Timelock-rescue vaults}

Take \textbf{Rewind Bitcoin}~\cite{rewind-bitcoin} as the exemplar. Funds sit in
a Bitcoin-native timelock vault; unlocking starts a multi-day countdown; if an
unauthorized unlock is triggered, the owner \emph{or a trusted delegate} has that
window to press ``Rescue'' and sweep to a cold panic address.

Against \emph{remote} theft it is sound: a thief who steals keys trips the
countdown, the owner notices, and rescues. But the spend capability sits behind
\emph{only a delay}, with keys on the seized device and no recall floor --- so a
wrench attacker who seizes the device \emph{does} hold a feasible path (unlock,
wait out the countdown). That is a race, in the sense of Lemma~\ref{lem:drl}.
Rewind's answer is exactly the second route of Remark~\ref{rem:reach}: it puts
the winning racer out of $\Attacker$'s reach --- a \emph{remote delegate} the
attacker cannot find or eliminate presses Rescue --- so the attack fails
cleanly. This is a legitimate clearance, but the remote-racer kind: its cost is
that \textbf{custody is no longer individual}.

\begin{remark}[When the escape closes]
The remedy holds only while the delegate is genuinely remote. If the delegate is
a friend who happens to be visiting during the attack, \emph{both} problems
apply at once --- custody was already non-individual, and the racer is now
co-located and reachable --- so the design becomes deadly-race-susceptible
again. The user is thus forced into an awkward corner: trust someone they can
rarely be near, and accept a perverse incentive to avoid physical proximity to a
trusted friend.
\end{remark}

\subsection{Great Wall, and the honest comparison}

Great Wall clears by the \emph{other} route: the secret is tacit and never on
the device (Assumption~\ref{ass:tkba}, Theorem~\ref{thm:floor}), so a seizure
yields nothing feasible --- there is no racer to reach, and the time-lock is
only a delay \emph{on top of} an already-clean failure. Custody stays
individual. The two designs therefore clear the same bar by the two different
routes of Remark~\ref{rem:reach}:
\begin{center}\small
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\linewidth}{@{}l l X@{}}
\toprule
\textbf{Design} & \textbf{Clearance route} & \textbf{Cost / consequence} \\
\midrule
Timelock-rescue (Rewind) & Remove reach over racer & Remote delegate $\Rightarrow$ \emph{shared} custody; escape closes if delegate co-located \\
Great Wall (orbit)       & Remove the race         & Tacit secret, $\ge \sftstar$ floor $\Rightarrow$ custody stays \emph{individual} \\
\bottomrule
\end{tabularx}
\end{center}
\noindent ``Put the racer out of reach'' versus ``leave no race to run'' is the
honest comparison. Other designs slot onto the same axis: plausible-deniability
and duress-PIN schemes fail Assumption~\ref{ass:kerckhoffs} (an educated
$\Attacker$ persists past the decoy); Shamir-only social recovery moves reach
onto guardians; multisig-by-geography attempts a weak form of the second route.

% ════════════════════════════════════════════════════════════════════════════
\section{Quantum note}
\label{sec:quantum}
% ════════════════════════════════════════════════════════════════════════════

A few-minutes memory-hard $\Hhard$ per element also defeats
Grover~\cite{grover1996}: a quantum search over an $n$-bit space needs
$\sim 2^{n/2}$ \emph{coherent} evaluations of the memory-hard oracle, which is
impractical for an hours-scale Argon2d barrier. Hence sub-256-bit standards
(96 or 128 bits per stage) are quantum-defensible \emph{without} a 256-bit seed
--- the memory-hardness that buys the $\sftstar$ floor classically also caps the
quantum speed-up.

% ════════════════════════════════════════════════════════════════════════════
\section{Limitations and scope}
\label{sec:limits}
% ════════════════════════════════════════════════════════════════════════════

Out of scope for this model: adversarial-agent scenarios (testator/heir mutual
distrust, malicious interference with rotation); device side-channels (timing,
EM, acoustic) during active tacit recall; long-horizon cryptographic erosion
(century-plus hardness of the underlying primitives and of Argon2 parameters
against future hardware); and mass on-chain correlation beyond the privacy of
standard taproot outputs and private channels.

Two scoping notes bear repeating. First, the framework fixes a \emph{bar}
(Principle~\ref{prin:nga}); it does not claim Great Wall is the unique
construction that clears it. Second, the residual window of
\S\ref{sec:residual} is a genuine, bounded gray sliver, argued to be
incentive-safe rather than eliminated --- we do not over-claim it away.

% ════════════════════════════════════════════════════════════════════════════
\section{Conclusion}
% ════════════════════════════════════════════════════════════════════════════

The Deadly Race turns ``graceful degradation'' from a virtue into a liability
whenever the degraded state is a feasible-but-slower path to the secret: by
Lemma~\ref{lem:drl}, that state is a race, and the race pays an assassination
incentive. The No-Gray-Area Principle is the resulting design bar, and the
reachability remark shows there are exactly two honest ways to clear it. The
Great Wall orbit clears it by removing the race entirely --- an $\sftstar$ floor
from every seizable state (Theorem~\ref{thm:floor}) --- and so keeps custody
individual, where timelock-rescue vaults clear the same bar by removing the
attacker's reach at the cost of a trusted third party.

\paragraph{Open items for the full draft.}
Fully game-based definitions of NNPL, the Lemma, and the Principle with an
explicit adversary game and a reduction for the $\sftstar$ floor; a quantitative
$\Hhard$ per-evaluation calibration tying S1/S2 to hardware; a precise
game-based definition of ``coercion-resistance'' that the Principle implies; and
an empirical grounding of the residual-window argument against the wrench-attack
registry~\cite{lopp-attacks}.

% ════════════════════════════════════════════════════════════════════════════
\bibliographystyle{plain}
\bibliography{references}

\end{document}
